Obtain metadata from Crossref Dump

### 2020-06-14 analysis/002_cr_els_matching.Rmd
prepare parsing for invoice data

```{r}
els_jns_df <- readr::read_csv(here::here("data", "elsevier_apc_list.csv"))
els_jn_hybrid <- els_jns_df %>% 
  filter(oa_type == "Hybrid")
bq_els <- bq_table_create(
  "api-project-764811344545.cr_dump_march_20.elshybrid",
  fields =  els_jn_hybrid,
  friendly_name = "Elsevier hybrid journals May 2020",
  description = "The data was extracted from Elsevier APC pricing list, 
    downloaded 30 May 2020"
)
bq_table_upload(bq_els, els_jn_hybrid)
```

@@

>>>>

```{r}
els_jns_df <- readr::read_csv(here::here("data", "elsevier_apc_list.csv"))
els_jn_hybrid <- els_jns_df %>% 
  filter(oa_type == "Hybrid")
if(!bq_table_exists("api-project-764811344545.cr_dump_march_20.elshybrid")) {
bq_els <- bq_table_create(
  "api-project-764811344545.cr_dump_march_20.elshybrid",
  fields =  els_jn_hybrid,
  friendly_name = "Elsevier hybrid journals May 2020",
  description = "The data was extracted from Elsevier APC pricing list, 
    downloaded 30 May 2020"
)
bq_table_upload(bq_els, els_jn_hybrid)
} else {
  NULL
}
```

@@

A few records have a date formats without day, which is used for the delayed calculation. We should therefore allow for a delay of up to  30 days.

```{r}
els_license_delay %>%
  filter(delay_in_days < 31) 
```

### Download open access articles in hybrid journals

```{sql, connection=con, output.var="els_hybrid_articles"}
SELECT *
FROM `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`, unnest(license) as license
WHERE (REGEXP_CONTAINS(license.URL, 'creativecommons') AND license.content_version = 'vor') AND 
  (issued_year BETWEEN 2015 and 2019) AND
  license.delay_in_days < 31
```

Backup

```{r}
require(jsonlite)
jsonlite::stream_out(els_hybrid_articles, file(here::here("data", "els_hybrid_articles.json")))
```
